Reliability Demonstration of A Novel Randomized Measurement and Verification Method for Switchable Control Retrofit Using Large-scale Public Dataset

### 2024-09-21 code/manuscript.Rmd
Updated result section

```{r tidysite, fig.cap = "Site summary of the tidy building subset", fig.width=8, fig.height=8}

@@

```{r chwst, fig.cap = "Proposed chilled water supply temperature reset based on outdoor temperature", fig.width=6, fig.height=4}

@@

| Parameter              | Description                                                      | Value |
|----------------|----------------------------------------|----------------|
| $\beta_{temp}$         | \% savings from setting $T_{interv}$ 1 °C higher than $T_{base}$ | 0.08  |
| $\beta_{occ}$          | \% savings adjustment during occupied hours                      | 1.2   |
| $\beta_{\text{unocc}}$ | \% savings adjustment during unoccupied hours                    | 0.8   |

@@

Although occupancy can be approximated in several ways in commercial
buildings, such as through counting check-in, or WIFI connections, or
monitoring indoor CO2 concentration as a proxy. However, it is not a
cost-efficient measures to add to the routine operation for most of the
buildings and there might be privacy concerns associated. The scenario
proposed hypothesize that during the baseline measurement period of the
target building, a floor of tenants moved out leaving the space
unoccupied for four months before new tenants moved in and this led to a
20% electricity decrease as a result. The M&V protocol only requires the
M&V analyst to fit a TOWT model so he/she only measures outdoor
temperature. Figure \@ref(fig:occchange) shows one example

@@

>>>>

```{r tidysite, fig.cap = "Site summary of the tidy building subset", fig.width=8, fig.height=6}

@@

```{r chwst, fig.cap = "Proposed chilled water supply temperature reset based on outdoor temperature", fig.width=8, fig.height=4}

@@

| Parameter              | Description                                                      | Value |
|-----------------|--------------------------------------|-----------------|
| $\beta_{temp}$         | \% savings from setting $T_{interv}$ 1 °C higher than $T_{base}$ | 0.08  |
| $\beta_{occ}$          | \% savings adjustment during occupied hours                      | 1.2   |
| $\beta_{\text{unocc}}$ | \% savings adjustment during unoccupied hours                    | 0.8   |

@@

Although occupancy can be approximated in several ways in commercial
buildings, such as through counting check-in, or WIFI connections, or
monitoring indoor CO2 concentration as a proxy. However, it is not a
cost-efficient measures to add to the routine operation for most of the
buildings and there might be privacy concerns associated. The scenario
proposed hypothesize that during the baseline measurement period of the
target building, a floor of tenants moved out leaving the space
unoccupied for four months before new tenants moved in and this led to a
20% electricity decrease as a result. The M&V protocol only requires the
M&V analyst to fit a TOWT model so he/she only measures outdoor
temperature. We showed one example in Figure \@ref(fig:occchange) where
from May 1st 2016 to August 31st 2016, the target building electricity
decreased 20% due to reduced occupancy. Thus subplot (a) shows measured
baseline with such change, which are then used for TOWT model fitting.
Starting from 2017, the occupancy returns normal and only intervention
strategy was measured and the projected baseline is the prediction
results from the fitted model. To demonstrate, we also plotted the
original measurements before adding the intervention effect as 'adjusted
baseline'. This assumes that we can accurately adjust the baseline in
the post-retrofit period on back-to-normal occupancy. Subplot (b) shows
that the fitted regression underestimate the true baseline condition
leading to underestimated savings.

@@

Figure \@ref(fig:occsavings) shows the normalized fractional savings
estimation accuracy comparison between the two M&V methods. To compare
which method is more robust to the applied occupancy change, a
difference-in-difference value is plotted in the figure. Each bar in the
plot represent the difference in the deviation of savings estimated by
the convention method and the randomized method:

$$
|S_{conv} - S_{true}| - |S_{rand} - S_{true}|
$$

In other words, a positive value indicate the randomized method provides
an estimation more aligned to the true target saving. Thus the plot
shows the randomized method shows uniformly superior robustness for all
sites. The red-dotted line shows the absolute deviation in savings
estimation by the randomized method as a reference for scaling. The
deviation is consistent with the distribution shown in Figure
\@ref(fig:tidysite) and thus further reinforce its robustness to
non-routine events.

```{r occsavings, fig.cap="Savings estimation accuracy comparison between two M&V methods with added occupancy change (with the site average difference-in-difference displayed at the bottom of each site).", fig.width=8, fig.height=4}
s <- 'S4'
dev_conv <- df_NRE_occ %>%
  filter(scenario == s) %>%
  filter(method != "rand") %>%
  group_by(name, site, scenario) %>%
  summarise(conv = abs(diff(savings))) %>%
  ungroup()

dev_rand <- df_NRE_occ %>%
  filter(scenario == s) %>%
  filter(method != "conv") %>%
  group_by(name, site, scenario) %>%
  summarise(rand = abs(diff(savings))) %>%
  ungroup()

dev_FS <- dev_rand %>%
  left_join(dev_conv, by = c("name", "site", "scenario")) %>% 
  mutate(diff_in_diff = conv - rand)

mean_diff <- dev_FS %>%
  group_by(site) %>%
  summarise(mean = round(mean(diff_in_diff), digits = 1),
            pos = round(n() / 2) + 1,
            .groups = 'keep')

dev_FS %>%
  ggplot(aes(group = site)) +
  geom_col(aes(x = name, y = diff_in_diff), position = "identity", alpha = 0.3) +
  facet_wrap(~site, nrow = 1, scales = "free_x") +
  scale_y_continuous(expand = c(0.1, 0),
                     breaks = breaks_pretty(n = 4), 
                     labels = number_format(suffix = "%")) +
  geom_text(data = mean_diff,
            aes(x = pos, y = -.5, group = site, label = paste0(mean, "%"))) +
  geom_line(aes(x = name, y = rand, color = "Absolute deviation of randomized method"), alpha = 0.5) +
  geom_point(aes(x = name, y = rand, color = "Absolute deviation of randomized method"), alpha = 0.5) +
  labs(x = NULL,
       fill = NULL,
       y = NULL,
       color = NULL, 
       title = "Difference-in-difference of fractional savings") +
  theme(panel.grid.major.y = element_line(color = "grey80", linewidth = 0.25),
        axis.text.x = element_blank(),
        legend.direction = "horizontal",
        legend.position = "bottom",
        plot.margin = margin(t = 2, r = 7, b = 2, l = 2, unit = "mm"))
```
